\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{geometry}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=0.7in, top=0.6in, right=0.7in, bottom=0.6in}

\setlist{noitemsep, topsep=2pt}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{#2} \\
  \end{tabular*}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% Personal Info
\newcommand{\name}{TANYA RATHORE}
\newcommand{\phone}{+91 7307633409}
\newcommand{\emaila}{tanyarathore7307@gmail.com}
\newcommand{\linkedin}{https://www.linkedin.com/in/tanya-rathore-26a653284/}
\newcommand{\github}{https://github.com/Tanya0294}
\newcommand{\portfolio}{https://tanyarathore-portfolio.netlify.app/}

\begin{document}

\begin{center}
\textbf{\Huge \name} \\[6pt]

\small
\faPhone\ \phone \quad
\href{mailto:\emaila}{\faEnvelope\ \emaila} \quad
\href{\linkedin}{\faLinkedin\ LinkedIn} \quad
\href{\github}{\faGithub\ GitHub} \quad
\href{\portfolio}{\faGlobe\ Portfolio}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
\item \small{Computer Science student and AI/ML enthusiast with hands-on experience in building and deploying machine learning models. Skilled in data preprocessing and model evaluation. Passionate about solving real-world problems using AI.}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {Jaypee University of Engineering and Technology}{2023 -- Present}
  {B.Tech in Computer Science Engineering}{Guna, MP}
\resumeSubheading
  {Gyan Sthali Academy}{2022}
  {CBSE (Class XII, Class X)}{India}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
  {Web Development Intern -- Trustique Assist Pvt. Ltd.}{May 2025 -- Jul 2025}
  {}{}
\resumeItemListStart
  \resumeItem{Developed 4--10 responsive web application screens using React, HTML and CSS, improving UI/UX and reducing user friction.}
  \resumeItem{Integrated REST APIs with backend systems to improve performance and data flow.}
  \resumeItem{Led digital transformation initiatives by prioritizing feature improvements with design and engineering stakeholders using direct user feedback.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
  {College Complaint Analyzer using NLP}{2026}
\resumeItemListStart
  \resumeItem{Developed a full-stack complaint management system with role-based authentication and analytics dashboards for Students, Teachers, and Administrators.}
  \resumeItem{Built an NLP pipeline using TF-IDF, NLTK, Logistic Regression, and Multinomial Naive Bayes for complaint classification, sentiment analysis, keyword extraction, and priority prediction.}
  \resumeItem{Trained ML models on 672 labeled complaints across 12 categories, achieving 80\% classification accuracy and 72\% priority prediction accuracy.}
\resumeItemListEnd

\resumeProjectHeading
  {AI Customer Support Email Agent}{2026}
\resumeItemListStart
  \resumeItem{Built an AI-powered customer support system using RAG to classify emails, retrieve relevant documents with FAISS, and generate context-aware responses.}
  \resumeItem{Implemented semantic search using Sentence Transformers with confidence-based routing to escalate low-confidence queries to human agents.}
  \resumeItem{Developed the backend using Python, FastAPI, LangChain, and Gemini/OpenAI APIs, automating repetitive support tasks and reducing manual effort.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
\item \textbf{Languages:} Python, C++, C, SQL
\item \textbf{AI/ML:} Machine Learning, NLP, TF-IDF, Scikit-learn, Pandas, NumPy, NLTK, Logistic Regression, Random Forest, Multinomial Naive Bayes
\item \textbf{Generative AI:} LangChain, RAG
\item \textbf{Dev \& Collaboration:} Git, GitHub, VS Code, REST APIs
\item \textbf{Core Concepts:} Data Structures and Algorithms
\end{itemize}

%-----------LEADERSHIP-----------
\section{Leadership \& Cross-Functional Impact}
\resumeSubHeadingListStart

\resumeSubheading
  {Co-Head of Logistics -- TEDxJUET 2026}{2026}
  {}{}
\resumeItemListStart
  \resumeItem{Led logistics for a 100--300 attendee TEDx event, coordinating 15+ volunteers across speakers, venue, and operations.}
  \resumeItem{Built on two years of event experience (TEDx 2025 Volunteer, ICMME 2025 Coordinator), demonstrating consistent growth into cross-functional leadership.}
\resumeItemListEnd

\resumeSubheading
  {Technical Joint Secretary \textbar\ Sports Joint Secretary}{2025 -- 2026}
  {Development Club \& CSI \textbar\ Sports}{}
\resumeItemListStart
  \resumeItem{Managed simultaneous leadership roles across technical and sports clubs while coordinating a 15-member student community.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
\item \small{Infosys Springboard \textbar\ GeeksforGeeks (GFG) \textbar\ Microsoft Badge}
\end{itemize}

\end{document}
